\vspace{1.0cm} \Large \bf Integrating influenza antigenic dynamics with molecular evolution

### 2013-12-06 flux.tex
Fix #41 - dimension typo.

We test model performance by constructing training datasets representing 90\% of the HI measurements for each of the four influenza lineages and test datasets representing the remaining 10\% of the measurements for each lineage. 
By fitting the BMDS model to the training dataset, we are able to predict HI titers in the test dataset and compare these predicted titers to observed titers.
We find that a two dimensional model has better predictive power than models of lower of higher dimension in all four influenza lineages (models 1--5; Table \ref{errortable}).
We find that this 2D model performs well, yielding an average absolute predictive error of between 0.78 and 0.91 log$_2$ HI titers across influenza lineages (model 2; Table \ref{errortable}), in line with the results of Smith et al.\ \cite{Smith04}.
Consequently, we specify a two dimensional model in all subsequent analyses.
The finding of a low-dimensional map across influenza lineages extends previous studies in A/H3N2 \cite{Smith04} and remains an interesting and fundamental empirical observation.

>>>>

We test model performance by constructing training datasets representing 90\% of the HI measurements for each of the four influenza lineages and test datasets representing the remaining 10\% of the measurements for each lineage. 
By fitting the BMDS model to the training dataset, we are able to predict HI titers in the test dataset and compare these predicted titers to observed titers.
We find that a two dimensional model has better predictive power than models of lower or higher dimension in all four influenza lineages (models 1--5; Table \ref{errortable}).
We find that this 2D model performs well, yielding an average absolute predictive error of between 0.78 and 0.91 log$_2$ HI titers across influenza lineages (model 2; Table \ref{errortable}), in line with the results of Smith et al.\ \cite{Smith04}.
Consequently, we specify a two dimensional model in all subsequent analyses.
The finding of a low-dimensional map across influenza lineages extends previous studies in A/H3N2 \cite{Smith04} and remains an interesting and fundamental empirical observation.
